Comparing vector-based and ACT-R memory models using large-scale datasets:\protect\\User-customized hashtag and tag prediction on Twitter and StackOverflow

### 2014-11-24 writeups/dissertation/dissertation.tex
foo

>>>>

\subsubsection{Dataset Descriptives}

The StackOverflow datasets had a much larger document size than the Twitter datasets overall.
There were on average 9 and 158 words in the title and body of a post for StackOverflow when sampled across the entire site. 
For Twitter, there were 13 words per tweet for the popular-users dataset and 18 for the popular-hashtags dataset.

The average number of tags per dataset was lower overall for Twitter.
For Twitter, authors used on average 1.1 hashtags per post for the popular-users dataset and 2.6 for the popular-hashtags dataset.
For StackOverflow, 2.8 tags were used on average across all posts on the site.

Since the document size and tags per document were higher for StackOverflow, the co-occurrence matrix for StackOverflow contained many more observations compared to Twitter.
Taking 1 million posts across the site, the StackOverflow co-occurrence matrix contained \num{835000000} total observations and \num{55000000} unique combinations of context words and tags.
For Twitter, when building a co-occurrence matrix for the popular-hashtags dataset from 3 million posts, the matrix contained \num{39000000} total observations and \num{4000000} unique combinations.

Hashtags for Twitter were both placed at the very end of the Tweet and embedded within the middle of the tweet.
For the popular-hashtags dataset, 11\% of hashtags were the last word in the Tweet and the rest were embedded within the tweet (not at the end).
Tags for StackOverflow were always placed at the very end of the post, since the author chose tags by placing them in a separate text field before submitting the post.

Each of the four Twitter popular-hashtags datasets contained the 400 most-popular hashtags at that time.
There was only a small amount of overlap between the hashtags chosen for each of the datasets.
Only 20\% of hashtags occurred two or more times across the four popular-hashtags datasets and the majority of those (66\%) occurred in only two of the four datasets.

The StackOverflow dataset contains many orders of magnitude fewer unique users than Twitter.
This means that the odds that the same user is sampled multiple times is less for the Twitter popular-hashtags dataset compared to all posts across the StackOverflow site.
For Twitter, an author contributed an average of 2 tweets to the popular-hashtags dataset.
Across the StackOverflow site, an author contributed 5 posts on average.

\paragraph{Tag Frequency Distribution}

\textcite{Stanley2013} found that the tag frequency for StackOverflow drops off sharply and approximately follows Zipf's Law.
The same effect was found for the 2014 StackOverflow dataset in this research and the two Twitter dataset subsets.
The results are depicted in Figure \ref{figDescTagFreq}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{descr-tagFrequencyCount.pdf}}}
  \caption{
    Log-log plot of tag frequency versus rank for the StackOverflow dataset and Twitter popular-users and popular-hashtags dataset subsets.
    Rank was assigned to each unique tag after ordering by tag frequency (most frequent given smallest rank).
}
  \label{figDescTagFreq}
\end{figure}

Tag frequency for StackOverflow and Twitter follow a similar Zipf's Law pattern, where tag use drops off sharply after moving away from the most popular tags.
However, none of the three distributions follow Zipf's Law perfectly, since none of the plots show perfectly linear lines.
Nonetheless, using three separate linear models to fit the data for the three distributions captures 96\% of the variance.
So these log-log plots are mostly linear, and both StackOverflow and Twitter closely follow Zipf's Law for tag use frequency.
